Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-12 paper/aldebaran.tex
second paragraph

%Stellar properties can be determined with the average seismic measures and effective temperature \teff.  A set of scaling relations exist that illustrate the constraint the global asteroseismic measures provide.  These scaling relations are understood to be approximate but never the less are commonly used for radius $R$, mass $M$, and surface gravity $g$:
Global asteroseismic parameters can be used to estimate the radius $R$, mass $M$, and surface gravity $g$ of stars when combined with an estimate of the effective temperature \teff\ through so-called scaling relations:

>>>>

%Stellar properties can be determined with the average seismic measures and effective temperature \teff.  A set of scaling relations exist that illustrate the constraint the global asteroseismic measures provide.  These scaling relations are understood to be approximate but never the less are commonly used for radius $R$, mass $M$, and surface gravity $g$:
These parameters can be used to estimate the radius $R$, mass $M$, and surface gravity $g$ of stars when combined with an estimate of the effective temperature \teff\ through so-called scaling relations:
